Contextual Combinatorial Cascading Bandits

### 2016-02-05 contextual combinatorial cascading bandits.tex
modify

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{combinatorial cascading bandits, context information, position discounts}

@@

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion. In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
We consider position discounts in the list order, so that the agent's reward is discounted depending on the position where the stopping criterion is met.
%We formulate this problem in a general contextual combinatorial cascading bandit setting.
We then propose a UCB-type algorithm, C$^3$-UCB, for this problem and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and give finer analysis for two special cases. 
Our work generalizes existing studies in several directions, including contextual information,
	position discounts, and a more general cascading bandit model.
Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.

@@

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time. A recent work \cite{qin2014contextual} (referred to as `C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their feedback is more informative than ours. We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.

@@

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent. Each feature vector combines the information of the user and the corresponding base arm. For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = u_t v_a^{\top}$ , the outer-product of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$. (See Section \ref{sec:movie} for an application.) Denote $x_t = (x_{t,a})_{a \in E}$ as all context information at time $t$. Then the learning agent recommends a feasible action $\bA_t=( \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t ) \in \cS$ to the user. In the cascading feedback models, the user checks from the first item of recommended action and stops at the $\bO_t$-th item under some stopping criterion. For example, in recommender systems, the stopping criterion might be that the user finds the first attractive item. Then the learning agent observes the weights of first $\bO_t$ base arms in $\bA_t$, denoted by $\bw_t(\ba_k^t), k \leq \bO_t$.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains feedback information at all time $s < t$, as well as context information at time $t$. Each arm $a$ has a weight $\bw_t(a)$, representing the ``quality'' to the user at time $t$. Given history $\cH_t$, we assume that $\bw_{t}(a)$'s are mutually independent random variables with expectation
\begin{equation} % eq:expectation
\label{eq:expectation}
\EE[\bw_{t}(a) | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Denote by 
$$
w_{t,a} = \theta_{\ast}^{\top} x_{t,a}
$$
the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $b \in \RR$, 
$$
\EE[\exp(b(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(b^2 R^2 / 2).
$$

@@

\begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
	(sketch) %The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging because of contextual information and position discounts $\gamma_k, k \leq K$. 
	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. We first employ the monotonicity and $B$-Lipschitz continuity of $f$ to upper bound regret as follows.
	\begin{equation}
		\label{eq:regretDeduction}
		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}^{-1}}.
	\end{equation}
	As $\bV_t$ contains only information of observed base arms, our UCB-type algorithm guarantees the sum of the first $\bO_t$ items in the right of Ineq. \ref{eq:regretDeduction} to be small, with the leftover sum (from $\bO_t + 1$ to $|\bA_t|$) out of control. We cope with this by a reduction to the case that $\bO_t = |\bA_t|$.
	%However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \nonumber\\
    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\nonumber\\
    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right]. \label{eq:ot=at}.
    \end{align}
    Combining \ref{eq:regretDeduction} and \ref{eq:ot=at} gives an upper bound of $R^{\alpha}(n)$ in terms of $\sum_{t=1}^n \sum_{k=1}^{\abs{\bO_t}} \gamma_k\norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$. The next Lemma upper bounds the sum of norms squared.
    %the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then for any time $t$,
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right).
    	$$
    \end{lemma}
    The claimed result thus follows. See the Appendix for a complete proof.
\end{proof}

@@

Now let us define a function $f: \cS \times [0,1]^E \to [0,1]$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{equation}
\label{eq:OrRewardFunc}
f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). 
\end{equation}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in the Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We thus have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

If we define a function $f : \cS \times [0,1]^E \to [0,1]$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS \text{ and } w = (w(1), \ldots, w(L))$ by
\begin{equation}
	\label{eq:AndRewardFunc}
	f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\end{equation}
then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, w_t) = f(\bA_t, \theta_{\ast}^{\top}x_t)$. Next is our result for the conjunctive objective with an improved bound than Theorem \ref{thm:main}, with $p^{\ast}$ improved by $\alpha f^{\ast}$. In network routing problem, the $p^{\ast}$ is related with the bad paths, which can make the probability of observing the whole path very small, and $f^{\ast}$ is related with good paths, which makes $f^{\ast}$ usually large.

@@

	Then similar to the proof of Theorem \ref{thm:main} and by the Lemma \ref{lem:XNormSumEst}, we can prove this theorem. See the Appendix for the complete proof.
\end{proof}

@@

The combinatorial cascading bandit \cite{kveton2015combinatorial} has a setting similar to ours in Section \ref{sec:conj}, but theirs has no contextual information or position discounts (i.e. all $\gamma_k = 1$). So our setting in Section \ref{sec:conj} is more general, but our regret bound is of order $O\left(\frac{d}{f^*}\sqrt{nK}\ln(n)\right)$, which has an additional term $\sqrt{\frac{d\ln(n)}{f^*}}$ compared to their result. The loss is because to handle the context information and obtain a confidence ellipsoid of $\theta_{\ast}$, we used the technique of linear bandits \cite{abbasi2011improved}, whose regret bound has an additional term of $O(\sqrt{d\ln(n)})$ than the standard stochastic MAB bound $O(\sqrt{nd\ln(n)})$. A similar comparison can be made between our Section \ref{sec:disj} and Section 2.3 of \cite{kveton2015combinatorial}.

@@

Our algorithm also applies to the setting of \cite{chen2013combinatorial} by allowing context information. Note the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notation) will be triggered.

@@

In the first experiment, we compare $C^3$-UCB to {\it CombCascade} on synthetic problems. This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user. At first, we randomly choose a $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$. Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the context information for arm $a$. This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{1}{2}(\theta^{\top}x'_{t,a} + 1) \in [0,1]$. Next we generate the weight for arm $a$ at time $t$ by a random sample from the Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.

We conduct experiments in four settings. Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items. The first two are of disjunctive objective where the learning agent observes a prefix of the chosen $K$ items until the first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$. Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order. The regrets are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the context information.

@@

\begin{figure}
	\centering
	\subfigure[$\gamma = 1$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
	\subfigure[$\gamma = 0.9$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
	\caption{Rewards on MovieLens, L=200, K=4, d=5}
	\label{fig:movielens} % 用于交叉引用
\end{figure}

@@

The Learning problem is formulated as follows. There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$. Next, we split $A$ as $H + F$ by putting $1$-entry in $A$ to $H$ or $F$ according to a Bernoulli distribution $\sim \mathrm{Ber}(p)$ for some fixed $p$. We regard $H$ as known information about history ``what users have watched'' and regard $F$ as future criterion. We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$. At every time $t$, we randomly choose a user $I_t \in [N_1]$. Then in the same spirit of \cite{li2010contextual}, we use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the context information for each movie $j$. The real weight of movie $j$ at time $t$, $\bw_t(j)$, is $F(I_t,m)$.

For this experiment, we randomly choose $L=200$ movies and recommend $K=4$ movies at each time. We experiment with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compare our algorithm with {\it CombCascade}. The results for rewards are shown in Fig.\ref{fig:movielens}. Our rewards increase the {\it CombCascade} ones by $9.2\%$ and $17.74\%$ respectively, which demonstrate the advantage to involve contextual information in real applications.

@@

The ground set $E$ is the set of links in the network. Before learning, the environment randomly chooses a $d$-dimensional vector $\theta_* \in [0,1]^d$. At each time $t$, a pair of source and destination nodes are randomly chosen and the feasible action set $\cS_t$ at time $t$ contains all simple paths between the source and destination. Any edge $a$ in the set $\cS_t$ is assigned with a random $d$-dimensional contextual information vector $x_{t,a}$. Notice here both $\theta$ and $x$ have been processed like in Section \ref{sec:ExpSyn} such that $\theta_*^{\top}x \in [0,1]$. The weight for each edge $a$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$. Then the learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between source and destination nodes to maximize the expected reward in the conjunctive objective. We experiment on different position discounts. The regrets are shown in Fig.~\ref{fig:network} (a) (b).

@@

In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action is observed each time. We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions. The experiments conducted demonstrate the advantage to involve contextual information and position discounts. In the future, we would like to investigate on lower bound of the regret and cascading on graphs.

>>>>

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{combinatorial cascading bandits, contextual information, position discounts}

@@

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of contextual information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion. In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
We consider position discounts in the list order, so that the agent's reward is discounted depending on the position where the stopping criterion is met.
%We formulate this problem in a general contextual combinatorial cascading bandit setting.
We design a UCB-type algorithm, C$^3$-UCB, for this problem, prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in the general setting, and give finer analysis for two special cases. 
Our work generalizes existing studies in several directions, including contextual information, position discounts, and a more general cascading bandit model.
Experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.

@@

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. The paper \cite{li2010contextual} studied multi-armed bandit with contextual information, which recommends one item a time. A recent work \cite{qin2014contextual} (referred to as `C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their feedback is more informative than ours. We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.

@@

At time $t$, feature vectors $x_{t,a} \in \RR^{d \times 1}$ with $\norm{x_{t,a}}_2 \leq 1$ for every base arm $a \in E$ are revealed to the learning agent. Each feature vector combines the information of the user and the corresponding base arm. For example, suppose the user at time $t$ is characterized by a feature vector $u_t$ and the base arm $a$ has a feature vector $v_a$, then we can use $x_{t,a} = u_t v_a^{\top}$ , the outer-product of $u_t$ and $v_a$, as the combined feature vector of base arm $a$ at time $t$. (See Section \ref{sec:movie} for an application.) Denote $x_t = (x_{t,a})_{a \in E}$ as all contextual information at time $t$. Then the learning agent recommends a feasible action $\bA_t=( \ba_{1}^t,...,\ba_{\abs{\bA_t}}^t ) \in \cS$ to the user. In the cascading feedback models, the user checks from the first item of recommended action and stops at the $\bO_t$-th item under some stopping criterion. For example, in recommender systems, the stopping criterion might be that the user finds the first attractive item. Then the learning agent observes the weights of first $\bO_t$ base arms in $\bA_t$, denoted by $\bw_t(\ba_k^t), k \leq \bO_t$.

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains feedback information at all time $s < t$, as well as contextual information at time $t$. Each arm $a$ has a weight $\bw_t(a)$, representing the ``quality'' to the user at time $t$. Given history $\cH_t$, we assume that $\bw_{t}(a)$'s are mutually independent random variables with expectation
\begin{equation} % eq:expectation
\label{eq:expectation}
\EE[\bw_{t}(a) | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Denote by 
$$
w_{t,a} = \theta_{\ast}^{\top} x_{t,a}
$$
the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $b \in \RR$, 
$$
\EE[\exp(b(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(b^2 R^2 / 2).
$$

@@

\begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
	(sketch) %The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging because of contextual information and position discounts $\gamma_k, k \leq K$. 
	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. We first employ the monotonicity and $B$-Lipschitz continuity of $f$ to upper bound regret as follows.
	\begin{equation}
		\label{eq:regretDeduction}
		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}^{-1}}.
	\end{equation}
	As $\bV_t$ contains only information of observed base arms, our UCB-type algorithm guarantees the sum of the first $\bO_t$ items in the right of Ineq. \ref{eq:regretDeduction} to be small, with the leftover sum (from $\bO_t + 1$ to $|\bA_t|$) out of control. We cope with this by a reduction to the case that $\bO_t = |\bA_t|$.
	%However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \nonumber\\
    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\nonumber\\
    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right]. \label{eq:ot=at}.
    \end{align}
    Combining \ref{eq:regretDeduction} and \ref{eq:ot=at} gives an upper bound of $R^{\alpha}(n)$ in terms of $\sum_{t=1}^n \sum_{k=1}^{\abs{\bO_t}} \gamma_k\norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$. The next lemma upper bounds this sum of norms, \emph{squared}.
    %the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then for any time $t$,
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right).
    	$$
    \end{lemma}
    The claimed result follows from Cauchy-Schwartz inequality. See Appendix for a complete proof.
\end{proof}

@@

Now let us define a function $f: \cS \times [0,1]^E \to [0,1]$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{equation}
\label{eq:OrRewardFunc}
f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). 
\end{equation}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We thus have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

If we define a function $f : \cS \times [0,1]^E \to [0,1]$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS \text{ and } w = (w(1), \ldots, w(L))$ by
\begin{equation}
	\label{eq:AndRewardFunc}
	f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\end{equation}
then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, w_t) = f(\bA_t, \theta_{\ast}^{\top}x_t)$. Next is our result for the conjunctive objective, where the bound in Theorem \ref{thm:main} is improved with $p^{\ast}$ replaced by $\alpha f^{\ast}$. In network routing problem, the $p^{\ast}$ is related with the bad paths, which can make the probability of observing the whole path very small, and $f^{\ast}$ is related with good paths, which makes $f^{\ast}$ usually large.

@@

	Then similar to the proof of Theorem \ref{thm:main} and by the Lemma \ref{lem:XNormSumEst}, we can prove this theorem. See Appendix for the complete proof.
\end{proof}

@@

The combinatorial cascading bandit \cite{kveton2015combinatorial} has a setting similar to ours in Section \ref{sec:conj}, but theirs has no contextual information or position discounts (i.e. all $\gamma_k = 1$). So our setting in Section \ref{sec:conj} is more general, but our regret bound is of order $O\left(\frac{d}{f^*}\sqrt{nK}\ln(n)\right)$, which has an additional term $\sqrt{\frac{d\ln(n)}{f^*}}$ compared to their result. The loss is because to handle the contextual information and obtain a confidence ellipsoid of $\theta_{\ast}$, we used the technique of linear bandits \cite{abbasi2011improved}, whose regret bound has an additional term of $O(\sqrt{d\ln(n)})$ than the standard stochastic MAB bound $O(\sqrt{nd\ln(n)})$. A similar comparison can be made between our Section \ref{sec:disj} and Section 2.3 of \cite{kveton2015combinatorial}.

@@

Our algorithm also applies to the setting of \cite{chen2013combinatorial} by allowing contextual information. Note the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notation) will be triggered.

@@

In the first experiment, we compare $C^3$-UCB to {\it CombCascade} on synthetic problems. This problem is a contextual cascading bandit with $L=100$ items and $K=4$, where at each time $t$ the agent recommends $K$ items to the user. At first, we randomly choose a $\theta \in \RR^{d-1}$ with $\|\theta \|_2 = 1$ and let $\theta_* = (\frac{\theta}{2}, \frac{1}{2})$. Then at each time $t$, we randomly assign $x'_{t,a} \in \RR^{d-1}$ with $\|x'_{t,a}\|_2 = 1$ to arm $a$ and use $x_{t,a} = (x'_{t,a}, 1)$ to be the contextual information for arm $a$. This processing will guarantee the inner product $\theta_*^{\top}x_{t,a} = \frac{1}{2}(\theta^{\top}x'_{t,a} + 1) \in [0,1]$. Next we generate the weight for arm $a$ at time $t$ by a random sample from the Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$.

We conduct experiments in four settings. Under each setting, the learning agent chooses a set of $K$ items out of $L$ ground items. The first two are of disjunctive objective where the learning agent observes a prefix of the chosen $K$ items until the first one with weight $1$; the last two are of conjunctive objective where the learning agent observes from the first item until the first one with weight $0$. Notice that with $\gamma \leq 1$, the oracle selects a set of $K$ items with highest UCBs in their decreasing order. The regrets are shown in Fig.~\ref{fig:synthetic} and our algorithm outperforms {\it CombCascade} algorithm because they do not make use of the contextual information.

@@

\begin{figure}
	\centering
	\subfigure[$\gamma = 1$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
	\subfigure[$\gamma = 0.9$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
	\caption{Rewards on MovieLens, $L=200$, $K=4$, $d=5$}
	\label{fig:movielens} % 用于交叉引用
\end{figure}

@@

The learning problem is formulated as follows. There is a big sparse matrix $A \in \{0,1\}^{N_1 \times N_2}$ where $A(i,j) = 1$ denotes user $i$ has watched movie $j$. Next, we split $A$ as $H + F$ by putting $1$-entry in $A$ to $H$ or $F$ according to a Bernoulli distribution $\sim \mathrm{Ber}(p)$ for some fixed $p$. We regard $H$ as known information about history ``what users have watched'' and regard $F$ as future criterion. We use $H$ to derive feature vectors of both users and movies by SVD decomposition, $H = USM^{\top}$ where $U = (u_1; ...;u_{N_1})$ and $M = (m_1;...;m_{N_2})$. At every time $t$, we randomly choose a user $I_t \in [N_1]$. Then in the same spirit of \cite{li2010contextual}, we use $x_{t,j} = u_{I_t}m_j^{\top}$, the outer product of $u_{I_t}$ and $m_{j}$, as the contextual information for each movie $j$. The real weight of movie $j$ at time $t$, $\bw_t(j)$, is $F(I_t,m)$.

For this experiment, we randomly choose $L=200$ movies and recommend $K=4$ movies at each time. We experiment with both $\gamma=1$ (no position discount) and $\gamma=0.9$, and compare our algorithm with {\it CombCascade}. The results for rewards are shown in Fig.\ref{fig:movielens}. The rewards of our algorithms are higher than those of {\it CombCascade} by $9.2\%$ and $17.74\%$ (for $\gamma = 1$ and $0.9$, respectively), which demonstrate the advantage to involve contextual information in real applications.

@@

The ground set $E$ is the set of links in the network. Before learning, the environment randomly chooses a $d$-dimensional vector $\theta_* \in [0,1]^d$. At each time $t$, a pair of source and destination nodes are randomly chosen and the feasible action set $\cS_t$ at time $t$ contains all simple paths between the source and destination. Any edge $a$ in the set $\cS_t$ is assigned with a random $d$-dimensional contextual information vector $x_{t,a}$. Notice here both $\theta$ and $x$ have been processed like in Section \ref{sec:ExpSyn} such that $\theta_*^{\top}x \in [0,1]$. The weight for each edge $a$ is a sample from Bernoulli distribution with mean $\theta_*^{\top}x_{t,a}$. Then the learning agent recommends a feasible path $A = (a_1,...,a_{|A|})$ between source and destination nodes to maximize the expected reward in the conjunctive objective. We experiment on different position discounts. The regrets are shown in Fig.~\ref{fig:network} (a), (b).

@@

In this paper, we propose contextual combinatorial cascading bandits with position discounts, where each action is an ordered list and only a prefix of the action is observed each time. We propose a C$^3$-UCB algorithm and prove a cumulative regret bound for general reward functions and two special reward functions. The experiments conducted demonstrate the advantage to involve contextual information and position discounts. In future, we would like to investigate on lower bounds of the regret and cascading on general graphs.
